---
title: "Embedded Words in 2020"
author: "Sung Inkyung"
date: '2020 12 19 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggtext)
```
pal <- color("muted")(7)
plot_scheme(colour("muted")(7))

```{r}
bible <- readr::read_csv("C:/Users/inkyscope/Documents/projects/data/bible_kjv_new.csv")

```


```{r}
words_2020 <-  c("knowledge",  "understanding", "wisdom",
                 "humble", "pray", "faith", "grace")

bible_words <- bible %>% 
  select(book, text) %>% 
  unnest_tokens(word, text) %>% 
  filter(word %in% words_2020) %>% 
  count(book, word)
```


```{r}
set.seed(123)

axis_ <- tibble(axis_x = runif(211),
                 axis_y = runif(211))

df_words <- bible_words %>% 
  bind_cols(axis_) %>% 
  mutate(label = str_c(word, "\n",
                       book, "\n",
                       n))

p1 <- df_words %>% 
    ggplot() +
    geom_point(data = df_words, 
               aes(axis_x, axis_y, size = n), 
               colour =  "#ff4500",
               alpha = 0.7) +
    geom_point(data = df_words, 
               aes(axis_x, axis_y), 
               colour = "#170b07", #"#b2d4b2"
               size = 1.7 ) +
    geom_text(data = df_words %>% filter(n > 20),
              aes(axis_x, axis_y, 
                  label = label),
              size = 5, 
              fontface = "bold",
              color = "gray80") +
   scale_size(range = c(2, 70)) +
   xlim(-0.02, 1) +
   labs(title = "**W O R D S 2 0 2 0**",
       subtitle = "Words that have dwelled in my heart like a well-embedded nail while listening to Bible audio throughout 2020",
      caption = "**Graphic**: Sung Inkyung") +
  theme_minimal() +
  theme(legend.position = "none",
        plot.background = element_rect(fill = "#242120",
                                       color = NA),
        panel.background = element_rect(fill = "#242120",
                                        color = NA),
        plot.title = element_markdown(size = 36,
                                      color = "gray80",
                                      face = "bold",
                                      hjust = 0.5),
        plot.subtitle = element_text(size = 17, 
                                     color = "gray80",
                                    hjust = 0.5),
        plot.caption = element_markdown (size = 14,
                                         color = "gray80",
                                        hjust = .5),
        panel.grid.major  = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        plot.margin = margin(20, 20, 20, 20)) +
  ggsave(here::here("2020", "1219_Words_2020", "1219_EmbeddedWords_2020.png"), width = 34, height = 38, units = "cm")
    
```

